Deep mutational scanning of an H3 hemagglutinin can inform evolutionary forecasting of human H3N2 influenza virus

### 2017-12-03 paper/manuscript.tex
Add section headers to `.tex` file

\begin{abstract}
\comment{Some title ideas:
- Determination of lineage-specific mutational effects in hemagglutinin of seasonal H3N2 influenza virus evolution
- Experimental measurements of mutational effects to hemagglutinin reveal lineage-specific evolution of seasonal H3N2 influenza virus
- Understanding the effects of mutation to hemagglutinin in the context of seasonal H3N2 influenza virus evolution}
\end{abstract}

>>>>

\begin{abstract}
Abstract text.
\end{abstract}

\section*{INTRODUCTION}

\section*{RESULTS}
\label{sec:results}

\subsection*{Strategy for deep mutational scanning of an H3 hemagglutinin}

\subsection*{H3 site-specific amino-acid preferences}

\subsection*{Estimating mutational effects from an H3N2 phylogeny}

\subsection*{Comparing H1 and H3 preferences}

\section*{DISCUSSION}

\clearpage
\small

\section*{METHODS}
\label{sec:methods}
\subsection*{HA numbering}

\subsection*{Generation of HA codon mutant plasmid libraries}

\subsection*{Generation and passaging of mutant viruses}

\subsection*{Barcoded subamplicon sequencing}

\subsection*{Analysis of deep sequencing data}

\subsection*{Quantification of mutational effects and sequence preferences from an H3N2 phylogeny}

\subsection*{Data availability and source code}
Deep sequencing data are available from the Sequence Read Archive under BioSample accession \comment{add accession}.

\subsection*{ACKNOWLEDGMENTS}
We thank Sarah Hilton, Hugh Haddox...the Fred Hutch Genomics Core
Funding...
